Modeling Intervention Strategies for United States TB Control

### 2014-02-08 in_progress/presentations/paper/draft.tex
updated intro

Though compartmental, differential equation models 
Finally, a
population level, agent based implementation of the Hill Model was created, in
order to validate the Hill Model against the natural stochasticity present in
real world disease spread.

>>>>

Though compartmental, differential equation models are the most common strategy
when modeling large-scale diseases at the population level with minimal age
stratification, an alternative approach is to use an agent-based model. Agent
based models provide a more nuanced view of disease spread as they provide a
more biologically reasonable framework; however, they are often considered to be
computationally infeasible at population level. In this work, a stochastic,
agent-based model of US TB was implemented which was used at the population
level to both provide statistical verification of the Hill Model and to
demonstrate the computational feasibility of an agent-based modeling framework
for general disease modeling.
